---
author: MAXWELL SARPONG
title: "hotel bookings"
output: html_notebook
---

#-------- importing the datasets --------------------------------

```{r}
hotel <- read.csv("C:/Users/Big-Max/Downloads/hotel-booking-demand/hotel_bookings.csv")
```


# -------- glimpse of the data ----------------------------------
```{r}
head(hotel)
```


#--------- data types of the data -------------------------------
```{r}
sapply(hotel, class)
```

#--------- types of the hotel -------------------------
```{r}
summary(hotel$hotel)
```

#------- plotting the types of the hotel ----------------------
```{r}
library(ggplot2)
ggplot(data = hotel, aes(x = hotel, y= "count")) +
  geom_bar( stat="identity")+
  guides(fill = FALSE)
```

#--------- list of countries involved in the hotel -------------------------------------
```{r}
levels(hotel$country)
```

#------------- selecting the countries ----------------------------------
```{r}
library(sqldf)
country <- sqldf("select country from hotel")
country<- data.frame(country)
```

# ------------ plotting of the countries ---------------------------------
```{r}
library(rworldmap)
newmap <- getMap(resolution = "low")
plot(newmap, xlim = c(-20, 59), ylim = c(35,71), asp=1)
points(country, col = "blue", cex= .9)
```

#------------ arrival_date_month_to_the_hotel ------------------------------
```{r}
ggplot(data = hotel, aes(x = arrival_date_month, y= "count")) +
   geom_bar( stat="identity")
   
```


#--------- splitting the data ----------------------------------
```{r}
library(rsample)
split<- initial_split(hotel, prop = .7)
train <- training(split)
test <- testing(split)
```

#-------- create models ----------------------------------
```{r}
library(rpart)
model <- rpart(is_canceled~ ., data = train)
```

#------------- predict ----------------------------------
```{r}
pred <- predict(model, test, type="vector")
```

#------------- confusion matrix to proof model -------------------
```{r}
table(test$is_canceled, pred)
```

#------------ plotting the final bookings ----------------------
```{r}
library(ggplot2)
ggplot(data = train, aes(x = is_canceled, y= "count", fill= is_canceled)) +
  geom_bar( stat="identity")+
  guides(fill = FALSE)
  
```


# -------------- joining predicted values and hotel names ----------------
```{r}
names <- data.frame(pred, test$hotel)
```

# -------- final predictions -------------------------------------
```{r}
names
```
